\bf Mechanistic models for panel data: analysis of ecological experiments with four interacting species

### 2023-12-12 ms.Rnw
Update

{
\small
\begin{align}
&d S(t) = r F(t)\left(S(t)+\xi I(t)\right)dt - \theta_{S}S(t) dt - p f_{S} S(t) Pdt - \delta S(t)dt + S(t) d\zeta_{S}(t),\\
&d I(t) = p f_{S} S(t) Pdt - \theta_{I} I(t)dt - \delta I(t)dt + I(t) d\zeta_{I}(t),\\
&dF(t) = \alpha F(t)\left(1-\frac{F(t)}{K_F}\right)dt - \gamma F(t) \left(S(t)+\xi I(t)\right) dt - \delta F(t) dt + \mu dt + F(t) d\zeta_F(t),\\
&d P(t) = \beta d I(t)dt +  - f_{S} S(t) P(t)dt - f_{I} I(t) P(t)dt - \theta_{\mathrm{p}} P(t)dt - \delta P(t) dt + P(t) d\zeta_{P}(t),\\
&d\zeta_{S} \sim N\left(0, \sigma_{S}^{2}dt\right),\\
&d\zeta_{I} \sim N\left(0, \sigma_{I}^{2}dt\right),\\
&d\zeta_{F} \sim N\left(0, \sigma_{F}^{2}dt\right),\\
&d\zeta_{P} \sim N\left(0, \sigma_{P}^{2}dt\right).
\end{align}
}

@@

{
\small
\begin{align}
\begin{split}
&d S_n(t) = r_n F(t) \left(S_n(t)+\xi I_n(t)\right)dt - \theta_{S_n}S_n(t) dt - p_n f_{S_n} S_n(t) P(t)dt -\\
&\quad \quad \quad\delta S_n(t)dt + S_n(t) d\zeta_{S_n}(t),\\
\end{split}
\\
&d I_n(t) = p_n f_{S_n} S_n(t) Pdt - \theta_{I_n} I_n(t)dt - \delta I_n(t)dt + I_n d\zeta_{I_n}(t),\\
\begin{split}
&d S_i(t) = r_i F(t)\left(S_i(t)+\xi I_i(t)\right)dt - \theta_{S_i} S_i(t) dt - p_i f_{S_i} S_i(t) P(t)dt - \\
&\quad \quad \quad \delta S_i(t)dt + S_i(t) d\zeta_{S_i}(t),\\
\end{split}
\\
&d I_i(t) = p_i f_{S_i} S_i(t) P(t)dt - \theta_{I_i} I_i(t)dt - \delta I_i(t)dt + I_i(t) d\zeta_{I_i}(t),\\
\begin{split}
&dF(t) = \alpha F(t)\left(1-\frac{F(t)}{K_F}\right)dt - \gamma_n F(t) \left(S_n(t)+\xi I_n(t)\right) dt - \\
&\quad \quad \quad\gamma_i F(t) \left(S_i(t)+\xi I_i(t)\right) dt - \delta F(t) dt + \mu dt + F(t) d\zeta_F(t),\\
\end{split}
\\
\begin{split}
&d P(t) = \beta_n d_n I_n(t)dt + \beta_i d_i I_i(t)dt - f_{S_n} S_n(t) P(t)dt - f_{I_n} I_n(t) P(t)dt - f_{S_i} S_i(t) P(t)dt \\
&\quad \quad \quad- f_{\mathrm{I}_i} I_i(t) P(t)dt - \theta_{\mathrm{p}} P(t)dt - \delta P(t) dt + P(t) d\zeta_{P}(t),\\
\end{split}
\\
&d\zeta_{S_n} \sim N\left(0, \sigma_{S_n}^{2}dt\right),\\
&d\zeta_{I_n} \sim N\left(0, \sigma_{I_n}^{2}dt\right),\\
&d\zeta_{S_i} \sim N\left(0, \sigma_{S_i}^{2}dt\right),\\
&d\zeta_{I_i} \sim N\left(0, \sigma_{I_i}^{2}dt\right),\\
&d\zeta_{F} \sim N\left(0, \sigma_{F}^{2}dt\right),\\
&d\zeta_{P} \sim N\left(0, \sigma_{P}^{2}dt\right).
\end{align}
}

@@

\begin{align}
&d S_n=r_n S_n dt- \theta_{S_n}S_n dt -\delta S_ndt + S_n d\zeta_{S_n}, \\
&d S_i=r_i S_i dt- \theta_{S_i} S_i dt -\delta S_idt + S_i d\zeta_{S_i}, \\
&dF=\alpha F\left(1-\frac{F}{K_F}\right)\cdot dt-\gamma_n F S_n \cdot dt - \gamma_i F S_i \cdot dt -\delta F \cdot dt+ \mu \cdot dt +F d \zeta_F.\\
&\zeta_F \sim N \left( 0, \sigma_F \right) \\
&\zeta_{S_n} \sim N \left( 0, \sigma_{S_n}  \right) \\
&\zeta_{S_i} \sim N \left( 0, \sigma_{S_i} \right) 
\end{align}

>>>>

{
\small
\begin{align}
&d S(t) = r F(t)\left(S(t)+\xi I(t)\right)dt - \theta_{S}S(t) dt - p f_{S} S(t) Pdt - \delta S(t)dt + S(t) d\zeta_{S},\\
&d I(t) = p f_{S} S(t) Pdt - \theta_{I} I(t)dt - \delta I(t)dt + I(t) d\zeta_{I},\\
&dF(t) = \alpha F(t)\left(1-\frac{F(t)}{K_F}\right)dt - \gamma F(t) \left(S(t)+\xi I(t)\right) dt - \delta F(t) dt + \mu dt + F(t) d\zeta_F,\\
&d P(t) = \beta d I(t)dt - f_{S} S(t) P(t)dt - f_{I} I(t) P(t)dt - \theta_{\mathrm{p}} P(t)dt - \delta P(t) dt + P(t) d\zeta_{P},\\
&d\zeta_{S} \sim N\left(0, \sigma_{S}^{2}dt\right),\\
&d\zeta_{I} \sim N\left(0, \sigma_{I}^{2}dt\right),\\
&d\zeta_{F} \sim N\left(0, \sigma_{F}^{2}dt\right),\\
&d\zeta_{P} \sim N\left(0, \sigma_{P}^{2}dt\right).
\end{align}
}

@@

{
\small
\begin{align}
% \begin{split}
&d S_n(t) = r_n F(t) \left(S_n(t)+\xi I_n(t)\right)dt - \theta_{S_n}S_n(t) dt - p_n f_{S_n} S_n(t) P(t)dt -\delta S_n(t)dt + S_n(t) d\zeta_{S_n},\\
% \end{split}
% \\
&d I_n(t) = p_n f_{S_n} S_n(t) Pdt - \theta_{I_n} I_n(t)dt - \delta I_n(t)dt + I_n d\zeta_{I_n},\\
% \begin{split}
&d S_i(t) = r_i F(t)\left(S_i(t)+\xi I_i(t)\right)dt - \theta_{S_i} S_i(t) dt - p_i f_{S_i} S_i(t) P(t)dt -  \delta S_i(t)dt + S_i(t) d\zeta_{S_i},\\
% \end{split}
% \\
&d I_i(t) = p_i f_{S_i} S_i(t) P(t)dt - \theta_{I_i} I_i(t)dt - \delta I_i(t)dt + I_i(t) d\zeta_{I_i}(t),\\
\begin{split}
&dF(t) = \alpha F(t)\left(1-\frac{F(t)}{K_F}\right)dt - \gamma_n F(t) \left(S_n(t)+\xi I_n(t)\right) dt - \gamma_i F(t) \left(S_i(t)+\xi I_i(t)\right) dt\\
&\quad \quad \quad- \delta F(t) dt + \mu dt + F(t) d\zeta_F,\\
\end{split}
\\
\begin{split}
&d P(t) = \beta_n d_n I_n(t)dt + \beta_i d_i I_i(t)dt - f_{S_n} S_n(t) P(t)dt - f_{I_n} I_n(t) P(t)dt - f_{S_i} S_i(t) P(t)dt \\
&\quad \quad \quad- f_{\mathrm{I}_i} I_i(t) P(t)dt - \theta_{\mathrm{p}} P(t)dt - \delta P(t) dt + P(t) d\zeta_{P},\\
\end{split}
\\
&d\zeta_{S_n} \sim N\left(0, \sigma_{S_n}^{2}dt\right),\\
&d\zeta_{I_n} \sim N\left(0, \sigma_{I_n}^{2}dt\right),\\
&d\zeta_{S_i} \sim N\left(0, \sigma_{S_i}^{2}dt\right),\\
&d\zeta_{I_i} \sim N\left(0, \sigma_{I_i}^{2}dt\right),\\
&d\zeta_{F} \sim N\left(0, \sigma_{F}^{2}dt\right),\\
&d\zeta_{P} \sim N\left(0, \sigma_{P}^{2}dt\right).
\end{align}
}

@@

\begin{align}
&d S_n(t)=r_n S_n(t) dt- \theta_{S_n}S_n(t) dt -\delta S_n(t)dt + S_n(t) d\zeta_{S_n}, \\
&d S_i(t)=r_i S_i(t) dt- \theta_{S_i} S_i(t) dt -\delta S_i(t)dt + S_i(t) d\zeta_{S_i}, \\
&dF=\alpha F(t)\left(1-\frac{F(t)}{K_F}\right)\cdot dt-\gamma_n F(t) S_n \cdot dt - \gamma_i F S_i \cdot dt -\delta F(t) \cdot dt+ \mu \cdot dt +F(t) d \zeta_F.\\
&\zeta_F \sim N \left( 0, \sigma_F^2dt\right) \\
&\zeta_{S_n} \sim N \left( 0, \sigma_{S_n}^2dt  \right) \\
&\zeta_{S_i} \sim N \left( 0, \sigma_{S_i}^2dt \right) 
\end{align}
